### 2021-12-11 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@fc87df909ef6e81e24c798d8fb75860abac8e193 🚀
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@a77780db763f722c3c0158980048f93335ff4df9 🚀

@@

\hypertarget{guidelines-for-prediction}{%
\section{Guidelines for prediction}\label{guidelines-for-prediction}}

@@

>>>>

In fig.~\ref{fig:biasmccinf}, we present the response of MCC and
informedness to (i) four levels of network connectance and (ii) a
gradient of training set bias, for the four component models as well as
the ensemble. All models reached a higher performance on more connected
networks, and using more biased training sets (with the exception of
ridge regression, whose informedness decreased in performance with
training set bias). In all cases, informedness was extremely high, which
is an expected consequence of the fact that this is the value we
optimized to determine the cutoff. MCC increased with training set bias,
although this increase became less steep with increasing connectance.
Interestingly, the ensemble almost always outclassed its component
models.

\begin{figure}
\hypertarget{fig:biasmccinf}{%
\centering
\includegraphics{figures/bias_mcc_inf.png}
\caption{TODO}\label{fig:biasmccinf}
}
\end{figure}

In fig.~\ref{fig:biasrocpr}, we present the same information as
fig.~\ref{fig:biasmccinf}, this time using ROC-AUC and PR-AUC. ROC-AUC
is always high, and does not vary with training set bias. On the other
hand, PR-AUC shows very strong responses, increasing with training set
bias. It is notable here that two classifiers that seemed to be
performing well (Decision Tree and Random Forest) based on their MCC are
not able to reach a high PR-AUC even at higher connectances. As in
fig.~\ref{fig:biasmccinf}, the ensemble outperforms its component
models.

\begin{figure}
\hypertarget{fig:biasrocpr}{%
\centering
\includegraphics{figures/bias_roc_pr.png}
\caption{TODO}\label{fig:biasrocpr}
}
\end{figure}

Based on the results presented in fig.~\ref{fig:biasmccinf} and
fig.~\ref{fig:biasrocpr}, it seems that informedness and ROC-AUC are not
necessarilly able to discriminate between good and bad classifiers
(although this result may be an artifact for informedness, as it has
been optimized when thresholding). On the other hand, MCC and PR-AUC
show a strong response to training set bias, and may therefore be more
useful at model comparison.

@@

The previous results revealed that the measure of classification
performance responds both to the bias in the training set \emph{and} to
the connectance of the network; from a practical point of view,
assembling a training set requires to withold positive information,
which in ecological networks are very scarce (and typically more
valuable than negatives, on which there is a doubt). For this reason,
across all values of connectance, we measured the training set bias that
maximized a series of performance measures. When this value is high, the
training set needs to skew positive in order to get a good model; when
this value is about 0.5, the training set needs to be artificially
balanced to optimize the model performance. These results are presented
in fig.~\ref{fig:optimbias}.

\begin{figure}
\hypertarget{fig:optimbias}{%
\centering
\includegraphics{figures/optim_mcc_inf.png}
\caption{TODO}\label{fig:optimbias}
}
\end{figure}

Interestingly, as long as the connectance of the network was above
\(\approx 0.1\), the optimal prevalence in the training set is 0.5,
\emph{i.e.} as many positives as negatives. Low connectance is usually
achieved for very large networks, due to the scaling relationship
between richness and links (MacDonald et al., 2020). Therefore, larger
networks may require \emph{more} biasing of the training set in order to
be optimally predicted, whereas smaller, more connected networks may
not. It is worth noting that the optimal bias for the training set
stabilizes at 0.5 regardless of connectance \emph{and} model \emph{and}
measure of model evaluation. \# Guidelines for prediction

INF because we trust positives more than negative, but check with MCC

PR-AUC

usually default to training set bias of 0.5

@@

\leavevmode\hypertarget{ref-MacDonald2020RevLin}{}%
MacDonald, A. A. M., Banville, F., \& Poisot, T. (2020). Revisiting the
Links-Species Scaling Relationship in Food Webs. \emph{Patterns},
\emph{1}(0). \url{https://doi.org/10.1016/j.patter.2020.100079}
